Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-12-18 main/doc/bdd_representation.tex
cleaned up and updated documentation

\section{BDD Representation}
\label{sec:bdd-representation}

Each domain containing $N$ elements is assigned $log_2 N$ BDD variables in the underlying BDD factory with contiguous IDs.
For instance,
domain {\tt F0} containing [2048..4096) elements will be assigned 12 variables with IDs (say) 59,60,61,62,63,64,65,66,67,68,69,70 and
domain {\tt Z0} containing [8..16) elements will be assigned 4 variables with IDs (say) 105,106,107,108.

If two domains are uninterleaved in the declared domain order in a Datalog program (i.e., {\tt \_} is used instead of {\tt x} between them),
then the BDD variables assigned to those domains are ordered in reverse order in the underlying BDD factory.
For instance, the BDD variable order corresponding to the declared domain order {\tt F0\_Z0} is (in level2var format)
``70,69,68,67,66,65,64,63,62,61,60,59,108,107,106,105".

If two domains are interleaved in the declared domain order in a Datalog program (i.e., {\tt x} is used instead of {\tt \_} between them),
then the BDD variables assigned to those domains are still ordered in reverse order of IDs in the underlying BDD factory,
but they are also interleaved.
For instance, the BDD variable order corresponding to the declared domain order {\tt F0xZ0} is (in level2var format)
``70,108,69,107,68,106,67,105,66,65,64,63,62,61,60,59".

>>>>

\section{BDD representation}
\label{sec:bdd-representation}

Each domain containing N elements is assigned log2(N) BDD variables in the underlying BDD factory with contiguous IDs.
For instance,
domain {\tt F0} containing [128..256) elements will be assigned 8 variables with IDs (say) 63,64,65,66,67,68,69,70 and
domain {\tt Z0} containing [8..16) elements will be assigned 4 variables with IDs (say) 105,106,107,108.

If two domains are uninterleaved in the declared domain order in a Datalog program (i.e., {\tt \_} is used instead of {\tt x} between them),
then the BDD variables assigned to those domains are ordered in reverse order in the underlying BDD factory.
For instance, the BDD variable order corresponding to the declared domain order {\tt F0\_Z0} is (in level2var format)
``70,69,68,67,66,65,64,63,108,107,106,105".

If two domains are interleaved in the declared domain order in a Datalog program (i.e., {\tt x} is used instead of {\tt \_} between them),
then the BDD variables assigned to those domains are still ordered in reverse order of IDs in the underlying BDD factory,
but they are also interleaved.
For instance, the BDD variable order corresponding to the declared domain order {\tt F0xZ0} is (in level2var format)
``70,108,69,107,68,106,67,105,66,65,64,63".

### 2010-12-18 main/doc/chord_sysprops.tex
cleaned up and updated documentation

\section{Chord System Properties}
\label{sec:chord-sysprops}

Users can use system properties to control \Chord's functionality.
The following properties are recognized by \Chord.
The separator for list-valued properties can be either a blank space, a comma, a colon, or a semi-colon.
Notation {\tt [<...>]} is used in this section to denote the value of the property named {\tt <...>}.

@@

This section describes basic properties of the given program that are required by program analyses in \Chord,
such as its main class, the location(s) of its class files and Java source files, and command-line arguments
to be used to run the program.

\begin{itemize}
\item
\code{chord.main.class} \\
{\bf Type:} class \\
{\bf Description:} Fully-qualified name of the main class of the given program (e.g., \code{com.example.Main}). \\
{\bf Note:} This property is required by virtually every task \Chord\ performs.

\item
\code{chord.class.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath of the given program.  It does not need to include boot classes (i.e., classes in \code{[sun.boot.class.path]}) or standard extensions (i.e., classes in {\tt .jar} files in directory \code{[java.home]/lib/ext/}). \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This property is required by virtually every task \Chord\ performs.

\item
\code{chord.src.path} \\
{\bf Type:} path \\
{\bf Description:} Java source path of the given program. \\
{\bf Default value:} {\tt ""}  \\
{\bf Note:} \Chord\ analyzes only Java bytecode, not Java source code.  This property is used only by the task of converting Java source files into HTML files by program analyses that need to present their analysis results at the Java source code level (by calling method \code{chord.program.Program.g().HTMLizeJavaSrcFiles())}.

\item
\code{chord.run.ids} \\
{\bf Type:} string list \\
{\bf Description:} List of IDs to identify runs of the given program. \\
{\bf Default value:} {\tt 0} \\
{\bf Note:} This property is used only when \Chord\ executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis.

\item
\code{chord.args.<id>} \\
{\bf Type:} string \\
{\bf Description:} Command-line arguments string to be used for the given program in the run having ID {\tt <id>}. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This property is used only when \Chord\ executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis.

\item
\code{chord.runtime.jvmargs} \\
{\bf Type:} string \\
{\bf Description:} Arguments to JVM which runs the given program. \\
{\bf Default value:} {\tt "-ea -Xmx1024m"} \\
{\bf Note:} This property is used only when \Chord\ executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis.
\end{itemize}

@@

This section describes properties that specify what task(s) \Chord\ must perform, 
such as computing the scope of the given program or running program analyses on the given program.

@@

\item
\code{chord.print.rels} \\
{\bf Type:} string list \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{[chord.out.dir]/<...>.txt} where {\tt <...>} denotes the relation name. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This task must be used with caution as certain program relations, albeit represented compactly as BDDs, may contain a large number (e.g., billions) of tuples, resulting in voluminous output when printed to a file.  See Section \ref{sec:tuning-datalog-analysis} for a more efficient way to query the contents of program relations (namely, by using the {\tt debug} target provided in file {\tt build.xml} in \Chord's {\tt main/} directory).

@@

This section describes properties of the JVM running \Chord, such as the working directory and various memory limits.

\begin{itemize}
\item
\code{chord.work.dir} \\
{\bf Type:} location \\
{\bf Description:} Working directory during \Chord's execution. \\
{\bf Default value:} current working directory

\item
\code{chord.props.file} \\
{\bf Type:} location \\
{\bf Description:} Properties file loaded by \code{[chord.main.dir]/build.xml}.  Any of the below properties, as well as other user-defined properties to be passed to \Chord\ (e.g., for user-defined analyses), may be set in this file.  Each relative (instead of absolute) path element in the value of any property named \code{chord.<...>.path} set in this file is converted to an absolute path element with respect to the directory containing this file. \\
{\bf Default value:} \code{[chord.work.dir]/chord.properties}

\item
\code{chord.max.heap} \\
{\bf Type:} string \\
{\bf Description:} Maximum memory size of JVM running \Chord. \\
{\bf Default value:} {\tt 1024m}

\item 
\code{chord.max.stack} \\
{\bf Type:} string \\
{\bf Description:} Maximum thread stack size of JVM running \Chord. \\
{\bf Default value:} {\tt 32m}

\item
\code{chord.jvmargs} \\
{\bf Type:} string \\
{\bf Description:} Arguments to JVM running \Chord. \\
{\bf Default value:} \code{"-showversion} \code{-ea} \code{-Xmx[chord.max.heap]} \code{-Xss[chord.max.stack]"}

\item
\code{chord.bddbddb.max.heap} \\
{\bf Type:} string \\
{\bf Description:} Maximum memory size of JVM running \bddbddb. \\
{\bf Default value:} {\tt 1024m} \\
{\bf Note:} Each program analysis written in Datalog is run in a separate JVM because there may be multiple invocations of the Datalog solver \bddbddb\ in a single run of \Chord\ and it is difficult to reset the global state of \bddbddb\ on each invocation.
\end{itemize}

@@

\item
\code{chord.scope.kind} \\
{\bf Type:} {\tt [dynamic|rta|cha]} \\
{\bf Description:} Algorithm to compute program scope.  Current choices include {\tt dynamic} (dynamic analysis), {\tt rta} (Rapid Type Analysis), and {\tt cha} (Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta}

@@

\item
\code{chord.std.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes inside the standard library whose method bodies must be treated as no-ops. \\
{\bf Default value:} \code{[chord.main.class.path]}

\item
\code{chord.ext.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes outside the standard library whose method bodies must be treated as no-ops. \\
{\bf Default value:} {\tt ""}

\item
\code{chord.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes whose method bodies must be treated as no-ops. \\
{\bf Default value:} \code{"[chord.std.scope.exclude],[chord.ext.scope.exclude]"}
\end{itemize}

@@

This section describes properties regarding program analyses executed by \Chord.

@@

\item
\code{chord.reuse.rels} \\
{\bf Type:} bool \\
{\bf Description:} Construct program relations from BDDs stored on disk (from a previous run of \Chord) whenever possible instead of re-computing them. \\
{\bf Default value:} {\tt false} 
% TODO: tell when this doesn't work

@@

\code{chord.std.check.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages inside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"sun.,com.sun.,com.ibm.jvm.,com.ibm.oti.,com.ibm.misc.,org.apache.harmony.,joeq.,jwutil.,java.,javax."}

@@

This section describes properties regarding program transformations performed by \Chord.

@@

This section describes properties that specify the amount of debug information that \Chord\ must produce during execution.

\begin{itemize}
\item
\code{chord.verbose} \\
{\bf Type:} int in the range [0..3] \\
{\bf Description:} Control the verbosity of logging during \Chord's execution. \\
{\bf Default value:} {\tt 2}

\item
\code{chord.bddbddb.verbose} \\
{\bf Type:} int in the range [0..5] \\
{\bf Description:} Control the verbosity of logging during the execution of JavaBDD (BDD library) and \bddbddb\ (Datalog solver). \\
{\bf Default value:} {\tt 0}

\item
\code{chord.save.maps} \\
{\bf Type:} bool \\
{\bf Description:} Write to file \code{[chord.bddbddb.work.dir]/<...>.map} when saving program domain named {\tt <...>}. \\
{\bf Default value:} {\tt true}  \\
{\bf Note:} This functionality is useful for debugging Datalog programs using the {\tt debug} target provided in file {\tt build.xml} in \Chord's {\tt main/} directory (see Section \ref{sec:tuning-datalog-analysis}).
\end{itemize}

@@

\begin{itemize}
\item
\code{chord.reuse.traces} \\
{\bf Type:} bool \\
{\bf Description:} Reuse dynamic traces computed by a previous run of \Chord\ if they exist. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} Property \code{chord.trace.kind} must be set to {\tt full} if this property is set to {\tt true}.

@@

\item
\code{chord.max.cons.size} \\
{\bf Type:} int \\
{\bf Description:} Maximum number of bytes over which events generated during the execution of any constructor in the given program may span. \\
{\bf Default value:} 50000000 \\
{\bf Note:} This property is relevant only for dynamic analyses which want events of the form {\tt NEW} $h$ $t$ $o$ to be generated (see Section \ref{sec:instr-events}).  The problem with generating such events at run-time is that the ID $o$ of the object freshly created by thread $t$ at object allocation site $h$ cannot be instrumented until the object is fully initialized (i.e., its constructor has finished executing).  Hence, \Chord\ first generates a ``crude dynamic trace", which has events of the form {\tt BEF\_NEW} $h$ $t$ and {\tt AFT\_NEW} $h$ $t$ $o$ generated before and after the execution of the constructor, respectively.  A subsequent pass generates a ``final dynamic trace", which replaces the {\tt BEF\_NEW} $h$ $t$ events by {\tt NEW} $h$ $t$ $o$ and discards the {\tt AFT\_NEW} $h$ $t$ $o$ events.  For this purpose, however, \Chord\ must buffer all events generated between the {\tt BEF\_NEW} and {\tt AFT\_NEW} events, and this property specifies the number of bytes over which these events may span.  If the actual number of bytes exceeds the value specified by this property (e.g., if the constructor throws an exception and the {\tt AFT\_NEW} event is not generated at all), then \Chord\ simply generates event {\tt NEW} $h$ $i$ $0$ (i.e., it treats the created object as having ID 0, which is the ID also used for {\tt null}).

@@

\item
\code{chord.dynamic.timeout} \\
{\bf Type:} int \\
{\bf Description:} The amount of time, in milliseconds, after which to kill the process running the given program during dynamic analysis, or -1 if the process must never be killed. \\
{\bf Default value:} -1
\end{itemize}

@@

@@

\item
\code{chord.bddbddb.work.dir} \\
{\bf Type:} location \\
{\bf Description:} Absolute location of the directory used by the Datalog solver \bddbddb\ as its input/output directory (namely, for program domain files {\tt *.dom} and {\tt *.map}, and program relation files {\tt *.bdd}). \\
{\bf Default value:} \code{[chord.out.dir]/bddbddb/}

>>>>

\section{Chord system properties}
\label{sec:chord-sysprops}

Users can use system properties to control Chord's functionality.
The following properties are recognized by Chord.
The separator for list-valued properties can be either a blank space, a comma, a colon, or a semi-colon.
Notation {\tt [<...>]} is used in this section to denote the value of the property named {\tt <...>}.

@@

This section describes basic properties of the given program that are required by program analyses in Chord,
such as its main class, the location(s) of its class files and Java source files, and command-line arguments
to be used to run the program.

\begin{itemize}
\item
\code{chord.main.class} \\
{\bf Type:} class \\
{\bf Description:} Fully-qualified name of the main class of the given program (e.g., \code{com.example.Main}). \\
{\bf Note:} This property is required by virtually every task Chord performs.

\item
\code{chord.class.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath of the given program.  It does not need to include boot classes (i.e., classes in \code{[sun.boot.class.path]}) or standard extensions (i.e., classes in {\tt .jar} files in directory \code{[java.home]/lib/ext/}). \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This property is required by virtually every task Chord performs.

\item
\code{chord.src.path} \\
{\bf Type:} path \\
{\bf Description:} Java source path of the given program. \\
{\bf Default value:} {\tt ""}  \\
{\bf Note:} Chord analyzes only Java bytecode, not Java source code.  This property is used only by the task of converting Java source files into HTML files by program analyses that need to present their analysis results at the Java source code level (by calling method \code{chord.program.Program.g().HTMLizeJavaSrcFiles())}.

\item
\code{chord.run.ids} \\
{\bf Type:} string list \\
{\bf Description:} List of IDs to identify runs of the given program. \\
{\bf Default value:} {\tt 0} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis.

\item
\code{chord.args.<id>} \\
{\bf Type:} string \\
{\bf Description:} Command-line arguments string to be used for the given program in the run having ID {\tt <id>}. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis.

\item
\code{chord.runtime.jvmargs} \\
{\bf Type:} string \\
{\bf Description:} Arguments to JVM which runs the given program. \\
{\bf Default value:} {\tt "-ea -Xmx1024m"} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis.
\end{itemize}

@@

This section describes properties that specify what task(s) Chord must perform, 
such as computing the scope of the given program or running program analyses on the given program.

@@

\item
\code{chord.print.rels} \\
{\bf Type:} string list \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{[chord.out.dir]/<...>.txt} where {\tt <...>} denotes the relation name. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This task must be used with caution as certain program relations, albeit represented compactly as BDDs, may contain a large number (e.g., billions) of tuples, resulting in voluminous output when printed to a file.  See Section \ref{sec:tuning-datalog-analysis} for a more efficient way to query the contents of program relations (namely, by using the {\tt debug} target provided in file {\tt build.xml} in Chord's {\tt main/} directory).

@@

This section describes properties of the JVM running Chord, such as the working directory and various memory limits.

\begin{itemize}
\item
\code{chord.work.dir} \\
{\bf Type:} location \\
{\bf Description:} Working directory during Chord's execution. \\
{\bf Default value:} current working directory

\item
\code{chord.props.file} \\
{\bf Type:} location \\
{\bf Description:} Properties file loaded by \code{[chord.main.dir]/build.xml}.  Any of the below properties, as well as other user-defined properties to be passed to Chord (e.g., for user-defined analyses), may be set in this file.  Each relative (instead of absolute) path element in the value of any property named \code{chord.<...>.path} set in this file is converted to an absolute path element with respect to the directory containing this file. \\
{\bf Default value:} \code{[chord.work.dir]/chord.properties}

\item
\code{chord.max.heap} \\
{\bf Type:} string \\
{\bf Description:} Maximum memory size of JVM running Chord. \\
{\bf Default value:} {\tt 1024m}

\item 
\code{chord.max.stack} \\
{\bf Type:} string \\
{\bf Description:} Maximum thread stack size of JVM running Chord. \\
{\bf Default value:} {\tt 32m}

\item
\code{chord.jvmargs} \\
{\bf Type:} string \\
{\bf Description:} Arguments to JVM running Chord. \\
{\bf Default value:} \code{"-showversion} \code{-ea} \code{-Xmx[chord.max.heap]} \code{-Xss[chord.max.stack]"}

\item
\code{chord.bddbddb.max.heap} \\
{\bf Type:} string \\
{\bf Description:} Maximum memory size of JVM running bddbddb. \\
{\bf Default value:} {\tt 1024m} \\
{\bf Note:} Each program analysis written in Datalog is run in a separate JVM because there may be multiple invocations of the Datalog solver bddbddb in a single run of Chord and it is difficult to reset the global state of bddbddb on each invocation.
\end{itemize}

@@

\item
\code{chord.scope.kind} \\
{\bf Type:} {\tt [dynamic|rta|cha]} \\
{\bf Description:} Algorithm to compute program scope.  The choices are {\tt dynamic} (dynamic analysis), {\tt rta} (Rapid Type Analysis), and {\tt cha} (Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta}

@@

\item
\code{chord.std.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes whose declared methods must be treated as no-ops.  Conventionally, this property is used to specify classes to be
excluded from the scope of all programs to be analyzed, e.g., classes in the JDK standard library.  \\
{\bf Default value:} \code{[chord.main.class.path]}

\item
\code{chord.ext.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes whose declared methods must be treated as no-ops.  Conventionally, this property is used to specify classes to be
excluded from the scope of specific programs to be analyzed. \\
{\bf Default value:} {\tt ""}

\item
\code{chord.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} Complete list of prefixes of names of classes whose declared methods must be treated as no-ops. \\
{\bf Default value:} \code{"[chord.std.scope.exclude],[chord.ext.scope.exclude]"}
\end{itemize}

@@

This section describes properties regarding program analyses executed by Chord.

@@

\item
\code{chord.reuse.rels} \\
{\bf Type:} bool \\
{\bf Description:} Construct program relations from BDDs stored on disk (from a previous run of Chord) whenever possible instead of re-computing them. \\
{\bf Default value:} {\tt false} 
% TODO: tell when this doesn't work

@@

\item
\code{chord.std.check.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages inside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"sun.,com.sun.,com.ibm.jvm.,com.ibm.oti.,com.ibm.misc.,org.apache.harmony.,joeq.,jwutil.,java.,javax."}

@@

This section describes properties regarding program transformations performed by Chord.

@@

This section describes properties that specify the amount of debug information that Chord must produce during execution.

\begin{itemize}
\item
\code{chord.verbose} \\
{\bf Type:} int in the range [0..6] \\
{\bf Description:} Control the verbosity of logging during Chord's execution. \\
{\bf Default value:} {\tt 2}

\item
\code{chord.save.maps} \\
{\bf Type:} bool \\
{\bf Description:} Write to file \code{[chord.bddbddb.work.dir]/<...>.map} when saving program domain named {\tt <...>}. \\
{\bf Default value:} {\tt true}  \\
{\bf Note:} This functionality is useful for debugging Datalog programs using the {\tt debug} target provided in file {\tt build.xml} in Chord's {\tt main/} directory (see Section \ref{sec:tuning-datalog-analysis}).
\end{itemize}

@@

\begin{itemize}
\item
\code{chord.instr.kind} \\
{\bf Type:} {\tt [offline|online]} \\
{\bf Description:} The kind of bytecode instrumentation.  The choices are offline and load-time. \\
{\bf Default value:} {\tt offline} \\

@@

\item
\code{chord.reuse.traces} \\
{\bf Type:} bool \\
{\bf Description:} Reuse dynamic traces computed by a previous run of Chord if they exist. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} Property \code{chord.trace.kind} must be set to {\tt full} if this property is set to {\tt true}.

@@

\item
\code{chord.dynamic.timeout} \\
{\bf Type:} int \\
{\bf Description:} The amount of time, in milliseconds, after which to kill the process running the given program during dynamic analysis, or -1 if the process must never be killed. \\
{\bf Default value:} -1

\item
\code{chord.max.cons.size} \\
{\bf Type:} int \\
{\bf Description:} Maximum number of bytes over which events generated during the execution of any constructor in the given program may span. \\
{\bf Default value:} 50000000 \\
{\bf Note:} This property is relevant only for dynamic analyses which want events of the form {\tt BEF\_NEW} $h$ $t$ $o$ to be generated (see Section \ref{sec:instr-events}).  The problem with generating such events at run-time is that the ID $o$ of the object freshly created by thread $t$ at object allocation site $h$ cannot be instrumented until the object is fully initialized (i.e., its constructor has finished executing).  Hence, Chord first generates a ``crude dynamic trace", which has events of the form {\tt BEF\_NEW} $h$ $t$ and {\tt AFT\_NEW} $h$ $t$ $o$ generated before and after the execution of the constructor, respectively.  A subsequent pass generates a ``final dynamic trace", which replaces each {\tt BEF\_NEW} $h$ $t$ event by {\tt BEF\_NEW} $h$ $t$ $o$.  For this purpose, however, Chord must buffer all events generated between the {\tt BEF\_NEW} and {\tt AFT\_NEW} events, and this property specifies the number of bytes over which these events may span.  If the actual number of bytes exceeds the value specified by this property (e.g., if the constructor throws an exception and the {\tt AFT\_NEW} event is not generated at all), then Chord simply generates event {\tt BEF\_NEW} $h$ $i$ $0$ (i.e., it treats the created object as having ID 0, which is the ID also used for {\tt null}).
\end{itemize}

@@

\item
\code{chord.reflect.file} \\
{\bf Type:} location \\
{\bf Description:} Absolute location of the file from/to which resolved reflection information is read/written. \\
{\bf Default value:} \code{[chord.out.dir]/reflect.txt}

@@

\item
\code{chord.bddbddb.work.dir} \\
{\bf Type:} location \\
{\bf Description:} Absolute location of the directory used by the Datalog solver bddbddb as its input/output directory (namely, for program domain files {\tt *.dom} and {\tt *.map}, and program relation files {\tt *.bdd}). \\
{\bf Default value:} \code{[chord.out.dir]/bddbddb/}

### 2010-12-18 main/doc/datarace.tex
cleaned up and updated documentation

\section{Datarace Analysis}
\label{sec:datarace}

Run the datarace analysis provided in \Chord\ by running the following command in \Chord's {\tt main/} directory:

\begin{quote}
\begin{verbatim}
prompt> ant -Dchord.work.dir=<...> -Dchord.run.analyses=datarace-java run
\end{verbatim}
\end{quote}

\noindent where directory {\tt <...>} contains a file named \code{chord.properties} which
defines properties \code{chord.main.class}, \code{chord.class.path}, and \code{chord.src.path}.
See Section \ref{sec:chord-sysprops} for the meaning of these properties.

Directory \code{main/examples/datarace_test/} provides a toy Java program on which you can run the datarace
analysis.
First run {\tt ant} in that directory (in order to compile the program's {\tt .java} files to
{\tt .class} files) and then run the above command in Chord's {\tt main/} directory
with {\tt <...>} replaced by \code{examples/datarace_test/}.
Upon successful completion, the following files should be produced in directory
\code{main/examples/datarace_test/chord_output/}:

>>>>

\section{Datarace analysis}
\label{sec:datarace}

Run the datarace analysis provided in Chord by running the following
command in Chord's {\tt main/} directory:

\begin{verbatim}
    prompt> ant -Dchord.work.dir=<...> -Dchord.run.analyses=datarace-java run
\end{verbatim}

\noindent where {\tt <...>} is the absolute path of a directory
containing a file named \code{chord.properties} which defines
properties \code{chord.main.class}, \code{chord.class.path}, and
\code{chord.src.path}.  See Section \ref{sec:chord-sysprops} for the
meaning of these properties.

Directory \code{main/examples/datarace_test/} provides a toy Java
program on which you can run the datarace analysis.  First run {\tt
  ant} in that directory (in order to compile the program's {\tt
  .java} files to {\tt .class} files) and then run the above command
in Chord's {\tt main/} directory with {\tt <...>} replaced by
\code{/.../examples/datarace_test/}.  Upon successful completion, the
following files should be produced in directory
\code{main/examples/datarace_test/chord_output/}:

### 2010-12-18 main/doc/deadlock.tex
cleaned up and updated documentation

\section{Deadlock Analysis}
\label{sec:deadlock}

@@

\noindent where directory {\tt <...>} contains a file named \code{chord.properties} which
defines properties \code{chord.main.class}, \code{chord.class.path}, and \code{chord.src.path}.
See Section \ref{sec:chord-sysprops} for the meaning of these properties.

Directory \code{main/examples/deadlock_test/} provides a toy Java program on which you can run
the deadlock analysis.
First run {\tt ant} in that directory (in order to compile the program's {\tt .java} files to
{\tt .class} files) and then run the above command in Chord's {\tt main/} directory with
{\tt <...>} replaced by \code{examples/deadlock_test/}.
Upon successful completion, the file \code{deadlocks.html} should be produced in directory
\code{main/examples/deadlock_test/chord_output/}.

>>>>

\section{Deadlock analysis}
\label{sec:deadlock}

@@

\noindent where {\tt <...>} is the absolute path of a directory
containing a file named \code{chord.properties} which defines
properties \code{chord.main.class}, \code{chord.class.path}, and
\code{chord.src.path}.  See Section \ref{sec:chord-sysprops} for the
meaning of these properties.

Directory \code{main/examples/deadlock_test/} provides a toy Java
program on which you can run the deadlock analysis.  First run {\tt
  ant} in that directory (in order to compile the program's {\tt
  .java} files to {\tt .class} files) and then run the above command
in Chord's {\tt main/} directory with {\tt <...>} replaced by
\code{/.../examples/deadlock_test/}.  Upon successful completion, the
file \code{deadlocks.html} should be produced in directory
\code{main/examples/deadlock_test/chord_output/}.
